---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  out.width = "100%"
)
```

**NOTE: This is a toy package created for expository purposes, for the second edition of [R Packages](https://r-pkgs.org). It is not meant to actually be useful. If you want a package for factor handling, please see [forcats](https://forcats.tidyverse.org).**


# foofactors

<!-- badges: start -->
<!-- badges: end -->

The goal of foofactors is to ...

## Installation

You can install the released version of foofactors from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("foofactors")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LakeHuron/foofactors")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(foofactors)
x <- factor(c("a", "b"))
y <- factor(c("c", "d"))
fbind(x, y)

x <- factor(c("a", "b", "a", "c", "c"))
fcount(x)
```

